Space-time plots

### 2016-04-02 Rmd/space-time.Rmd
Bulk commit of various changes, including library functions added. Edits to space-time.Rmd include near-final version of figure.

---
title: "Space-time plots"
author: "Lyndon Estes"
date: "December 3, 2015"
output: 
  html_document:
    toc: yes
---

# Space versus time analysis
```{r, eval = FALSE}
library(data.table)
library(raster)
library(sp)
require(splancs)
library(lmisc)
p_root <- set_base_path("ecoscales")
p_dat <- full_path(p_root, "external/data")
dat <- fread(full_path(p_dat, "merged-data.csv"), stringsAsFactors = FALSE)
setnames(dat, "DOI/title", "DOI")
dat <- dat[, names(dat)[1:20], with = FALSE]
unique(dat$DOI)  # 139
```

## Spatal and temporal data

### Scaling in log10 space
```{r}
i <- 0.000001
j <- rep(0, 15)
for(k in 1:length(j)) {
  i <- i * 10
  j[k] <- i
}
tdt <- data.table("scaleval" = j, "time" = j)
tdt[, tlog := log10(time)]

# label axis for time
taxis <- cbind.data.frame(
  c("Sec", "Min", "Hour", "Day", "Month", "Year", "Decade", "Century", 
    "Millenium", "10000"),  
  c(1 / (24 * 60 * 60), 1 / (24 * 60), 1 / 24, 1, 30, 365, 365 * 10, 
    365 * 100, 365 * 1000, 365 * 10000))
taxis <- data.table(taxis)
setnames(taxis, names(taxis), c("label", "days"))
taxis[, logdays := log10(days)]

rdt <- data.table("scaleval" = j, "area" = j^2)
rdt[, slog := log10(scaleval)]
rdt[, rlog := log10(area)]

adt <- data.table("area" = j)
adt[, alog := log10(area)]

@@

### Resolution versus extent, gridded
```{r,eval = FALSE}
rres <- 0.25
# # raster for resolution (x dimension) versus area (y dimension)
# # arst <- raster(xmn = -6, xmx = 9, ymn = -5, ymx = 10)
# rst <- raster(xmn = -5, xmx = 10, ymn = -5, ymx = 10)
# res(rst) <- rres
# # rst@crs <- CRS("")
# rst[] <- 1
# rst2 <- raster(xmn = 0, xmx = 10, ymn = 0, ymx = 10)
# # res(rst2) <- c(0.25, 0.25)
# res(rst2) <- rres
# # rst@crs <- CRS("")
# rst2[] <- 1
# plot(rst2)

resdat <- data.table(x = log10(dat$t_btwn_samp + 0.00001), 
                     y = log10(dat$plot_res))
# resdat[x < -5, x := -4.5]
# resdat[y < -5, y := -4.5]
resdat$n <- rep(1, nrow(resdat))
coordinates(resdat) <- ~x + y
# plot(resdat$x, resdat$y)
rx <- range(resdat$x)
# rx <- c(floor(rx[1]), c(ceiling(rx[2])))
rx <- round(rx / 0.5) * 0.5  # round to nearest 0.5
rxd <- length(seq(rx[1], rx[2], rres))  # 0.25))
ry <- range(resdat$y)
# ry <- c(floor(ry[1]), c(ceiling(ry[2])))
ry <- round(ry / 0.5) * 0.5  # round to nearest 0.5
ryd <- length(seq(ry[1], ry[2], rres))#0.25))

# length(seq(-5, 4, 0.25))

extdat <- data.table("x" = log10(dat$study_duration + 0.00001), 
                     "y" = log10(dat$sampled_area + 0.00001)) 
# extdat <- data.table("x" = log10(dat$study_span), 
#                      "y" = log10(dat$sampled_area)) 
# extdat[x < 0, x := 0]
# extdat[y < 0, y := 0]  # setting minima to 1 day and 1 ha
extdat$n <- rep(1, nrow(extdat))
coordinates(extdat) <- ~x + y
# plot(extdat$x, extdat$y)
ex <- range(extdat$x)
# ex <- c(floor(ex[1]), c(ceiling(ex[2])))
ex <- round(ex / 0.5) * 0.5  # round to nearest 0.5
ex[1] <- -5
exd <- length(seq(ex[1], ex[2], rres))#0.25))
ey <- range(extdat$y)
# ey <- c(floor(ey[1]), c(ceiling(ey[2])))
ey <- round(ey / 0.5) * 0.5  # round to nearest 0.5
eyd <- length(seq(ey[1], ey[2], rres))#0.25))

# set-up grid topologies
rgrd <- GridTopology(cellcentre.offset = c(rx[1], ry[1]) + 0.125, 
                     #cellsize = c(0.25, 0.25), cells.dim = c(rxd, ryd))
                     cellsize = c(rres, rres), cells.dim = c(rxd, ryd))
egrd <- GridTopology(cellcentre.offset = c(ex[1], ey[1]) + 0.125, 
                     #cellsize = c(0.25, 0.25), cells.dim = c(exd, eyd))
                     cellsize = c(rres, rres), cells.dim = c(exd, eyd))
# seq(0, 10, 10 / 59)

rst <- raster(xmn = rx[1], xmx = rx[2], ymn = ry[1], ymx = ry[2])
# rst <- raster(xmn = min(resdat$x), xmx = ceiling(max(resdat$x)), 
#               ymn = min(resdat$y), ymx = ceiling(max(resdat$y)))
res(rst) <- rres
# rst@crs <- CRS("")
rst[] <- 1
# plot(rst)
rst2 <- raster(xmn = ex[1], xmx = ex[2], ymn = ey[1], ymx = ey[2])
# rst2 <- raster(xmn = min(extdat$x), xmx = ceiling(max(extdat$x)), 
#               ymn = min(extdat$y), ymx = ceiling(max(extdat$y)))
res(rst2) <- rres
# rst@crs <- CRS("")
rst2[] <- 1
# plot(rst2)

# kernel densities
# resolution
ppoly <- as(extent(rst), "SpatialPolygons")
crds <- slot(slot(slot(ppoly, "polygons")[[1]], "Polygons")[[1]], "coords") 
kern1 <- spkernel2d(resdat, crds, h0 = 1, rgrd)
kgrid1 <- as(SpatialGridDataFrame(rgrd, data = data.frame(kern1)),
             "SpatialPixelsDataFrame")

# extent
ppoly <- as(extent(rst2), "SpatialPolygons")
crds <- slot(slot(slot(ppoly, "polygons")[[1]], "Polygons")[[1]], "coords") 
kern2 <- spkernel2d(extdat, crds, h0 = 1, egrd)
kgrid2 <- SpatialGridDataFrame(egrd, data = data.frame(kern2))

# rasterize
# space
rr <- raster(kgrid1)
rr[is.na(rr)] <- 0
# time
er <- raster(kgrid2)
er[is.na(er)] <- 0

# have a look
par(mfrow = c(2, 1))
plot(er, axes = FALSE, add = FALSE)
arg <- list(at = taxis$logdays, labels = taxis$label)
image(er, col = rev(terrain.colors(100)), axes = FALSE, xlab = "", ylab = "", 
      xlim = c(-5, 6))
axis(1, at = taxis$logdays, labels = taxis$label, las = 2)
axis(2, at = -5:10, las = 2)

# points(extdat$x, extdat$y)
plot(rr)
# points(resdat$x, resdat$y)

ers <- er
rrs <- rr
```

### Convert to rgb space and plot
```{r, eval = FALSE}
# As separate plots
png("paper/figures/res&extent2.png", width = 900, height = 450)
par(mfrow = c(1, 2), oma = c(0, 0, 0, 0), mar = c(4, 4, 4, 4))
plot(rrs, xlim = c(-5, 15), ylim = c(-5, 15), 
     xlab = "Sample interval - log10(days)", 
     ylab = "Plot resolution - log10(m^2)")
plot(ers, box = FALSE, xlim = c(-5, 15), ylim = c(-5, 15), 
     xlab = "Study duration - log10(days)", ylab = "Sampled area - log10(ha)")
dev.off()
```

>>>>

---
title: "Space-time plots"
author: "Lyndon Estes"
date: "December 3, 2015"
output: 
  html_document:
    toc: yes
    number_sections: true
    toc_depth: 3
---

# Space versus time analysis
```{r, eval = FALSE}
library(ecoscales)
library(readxl)
library(stringdist)
library(maptools)

p_root <- set_base_path("ecoscales")
p_dat <- full_path(p_root, "external/data/result")
# p_dat <- full_path(p_root, "external/data/")
# dat <- fread(full_path(p_dat, "merged-data.csv"), stringsAsFactors = FALSE)
dat <- as.data.table(read_excel(full_path(p_dat, "merged.xlsx")))
setnames(dat, "DOI/title", "DOI")
dat <- dat[, names(dat)[1:20], with = FALSE]
unique(dat$DOI)  # 139
```

## Spatal and temporal data 
### Adjustments
Prior to scaling the data in log10 space, we need to make some adjustments.

1. Time between samples has many 0 values because many observations are simply one-offs.  Set these to an arbitrarily large value which will represent clear separation on axis from high frequency studies

```{r, eval=FALSE}
# dat[t_btwn_samp > 0.000001 & t_btwn_samp < 0.001, ]
# dat[t_btwn_samp <0]
# dat[t_btwn_samp == 0, t_btwn_samp := 365 * 100000]  # interval adjust
# dat[study_duration > 365 * 1000]

### Inconsistency in study_duration - multiplying by N sites in many cases
# Paul a little bit, Ahmed, Chang. Jonathan a few places also. 
```

### Bootstrap on uncertainties

Just for the four main variables. Rules:

+ If `plot_res` and/or `n_sites` uncertain, then `sampled_area` must be. Recalculate using random draw within the uncertain variable 
+ If `t_btwn_samp` and/or `samp_duration` uncertain, do the same as above, but we have no variable for n repeats for calculating `study_duration`.

```{r, eval = FALSE}
svars <- c("plot_res", "n_sites", "sampled_area", "samp_duration",
           "t_btwn_samp", "study_duration")

sens <- gsub("\\\\", ";", dat$sensitivity)
sens <- gsub(", ", ";", gsub("; ", ";", sens))
sens <- tolower(sens)
sensl <- strsplit(sens, ";")
unique(unlist(sensl))

# sensul <- unlist(sensl)
# smatch <- adist(sensul, svars, partial = TRUE, ignore.case = TRUE)
# min_name <- apply(smatch, 1, min)
# matchs1s2 <- NULL  
# for(i in 1:nrow(smatch)) {  # i <- 10
#     s2i <- match(min_name[i], smatch[i, ])
#     s1i <- i
#     ms1s2 <- rbind(data.frame(s2i=s2i, s1i=s1i,
#                               s2name = svars[s2i],
#                               s1name = sensul[s1i],
#                               adist = min_name[i]), ms1s2)
# }
# # and we then can have a look at the results
# View(ms1s2)

sens2 <- gsub("plo_", "plot_", sens)  # fix this one
sens2 <- gsub("[[:blank:]]", "_", sens2)  # replace spaces with _

corrtab <- cbind(c("^res", "plo_res", "sample_area", "samples_area", 
                   "sampled area",
                   "t_btwn_samples", "t_btwn_sample", "t_btwn_samp_samp", 
                   "t_twn_samp", "t_btw_samp", "samp_duratiion", 
                   "sampling_duration", "sample_duration", 
                   "plot_resolution", "number_of_sites", 
                   "time_between_sampling", "plot_size", 
                   "time_between_samples", "samp_study", ":", " ", ";_"), 
                 c(svars[c(1, 1, 3, 3, 3, 5, 5, 5, 5, 5, 4, 4, 4, 1, 2,
                           5, 1, 5)], "samp;study", ";", ";", ";"))
for(i in 1:nrow(corrtab)) {
  sens2 <- gsub(corrtab[i, 1], corrtab[i, 2], sens2)
}
# gsub("[a-z]( )[a-z]", "_", sens[[228]])
# sens[[228]]
# sens2[is.na(sens2)]
sens2[is.na(sens2)] <- "none"
sensl2 <- lapply(1:length(sens2), function(x) strsplit(sens2[x], ";")[[1]])
# unique(unlist(sensl))
unique(unlist(sensl2))

# create a sensitivity table
senst <- do.call(cbind.data.frame, lapply(svars, function(x) {
  v <- sapply(sensl2, function(y) ifelse(any(y == x), 1, 0))
  # ifelse(is.na(v), 0, v)
}))
colnames(senst) <- c("res", "n", "sarea", "sampd", "tbtwn", "studyd")

# add column for uncertainty about n repeats
# senst$nrep <- rep(0, nrow(senst))

# i <- 300:305
# sensl2[i]
# senst[i, ]

# apply fixes (mostly to account for observer omissions)
# 1. if samp_duration != study_duration and t_btwn_samp == 0, set 
#    study_duration == samp_duration
# change made in dat
# dat[which(dat$t_btwn_samp == 0 & dat$study_duration == 1), ]
names(dat)
dat[t_btwn_samp == 0 & (study_duration != samp_duration), c(8:13), 
    with = FALSE]
# which(dat$t_btwn_samp == 0 & senst$studyd == 1)
dat[t_btwn_samp == 0 & study_duration == 1, 
    study_duration := samp_duration]
# dat[t_btwn_samp == 0 & study_duration == 1, ]

# 2. if samp_duration OR t_btwn_samp is uncertain, study_duration must also be. 
id <- which((senst$sampd == 1 | senst$tbtwn == 1) & senst$studyd == 0)
senst[id, "studyd"] <- 1  
# senst[id, ]

# but no real need to set it to 1 because it will get automatically perturbed
# via n_repeats

# which(dat$t_btwn_samp == 0 & dat$samp_duration == 1)
# which(dat$t_btwn_samp == 0 & dat$samp_duration == 1)
# which(dat$t_btwn_samp == 0 & senst$sampd == 1)

# 3. if study_duration is uncertain but t_btwn and samp_duration are not, treat
# both as uncertain
id <- which(senst$tbtwn == 0 & senst$sampd == 0 & senst$studyd == 1)
senst[id, c("sampd", "tbtwn")] <- 1
# senst[id, ]

# although it is possible that just n_repeats is uncertain, but more likely 
# that observers didn't note this is sensitive.

# id <- which(senst$tbtwn == 0 & senst$sampd == 0 & senst$studyd == 1)
# which(senst$sampd == 0 & senst$studyd == 1)
# dat[which(senst$sampd == 0 & senst$studyd == 1), ]

# 4. Can t_btwn_samps be 0 and study_duration be uncertain if samp_duration is 
# not?  No, it shouldn't be.

# note situations in which neither plot_res or n_samples are certain and 
# study_area is not
any(which(senst$res == 0 & senst$sarea == 1) %in% 
      which(senst$n == 0 & senst$sarea == 1))
which(senst$res == 1 & senst$n == 1 & senst$sarea == 1)
which(senst$res == 1 & senst$sarea == 1)
which(senst$n == 1 & senst$sarea == 1)
which((senst$res == 1 & senst$sarea == 1) | (senst$n == 1 & senst$sarea == 1))
```

### Run resampling with 
  - With 10% variation
  - With 20% variation
  - With 30%
  - Linked to calibration stdev

```{r, eval=FALSE}
# function to recalculate study_duration by finding hidden sampling frequency 
# variable from study_duration and samp_duration. 
recalc_duration <- function(study, samp, tbtwn) {
  ifelse(tbtwn == 0, samp, (study / samp) * samp)
}

# function to set t_btwn_samp to 365 * 100000 to indicate once-off studies 
# when t_btwn_samp == 0.  
to_infin_byond <- function(tbtwn) ifelse(tbtwn == 0, 365 * 10000, tbtwn)

# dat[, round(t_btwn_samp, 6) == 0]
# dat[1, n_repeats(t_btwn_samp, samp_duration, study_duration) * samp_duration]
# round(dat[, recalc_duration(study_duration, samp_duration)] - 
#         dat$study_duration, 8)

# set.seed(123)
# spct <- rnorm(1000, mean = 1, sd = 0.3)
# # hist(runif(1000, min = 0.8, max = 1.2))
# set.seed(123)

# hist(rgamma(100, 1, rate = 0.5))
# hist(rlnorm(100, 0.1, sd = 1))
# hist(rexp(100, rate = 2))

p <- 0.2
lapply(1:10, function(x, slen = 1, p = 0) {

  # a <- rnorm(1, mean = 1, sd = 0.3)
  # b <- rnorm(1, mean = 1, sd = 0.3)
  a <- runif(slen, min = 1 - p, max = 1 + p)  # plot_res perturb
  b <- runif(slen, min = 1 - p, max = 1 + p)  # n_sites perturb
  d <- runif(slen, min = 1 - p, max = 1 + p)  # samp_duration perturb
  e <- runif(slen, min = 1 - p, max = 1 + p)  # t_btwn_samp perturb

  dnew <- copy(dat[, .(plot_res, n_sites, sampled_area, samp_duration,
                       t_btwn_samp, study_duration)])
  dnew[which(senst$res == 1), plot_res := plot_res * a]
  dnew[which(senst$n == 1), n_sites := n_sites * b]
  dnew[, sampled_area := (plot_res * n_sites) / 10000]
  # plot(dnew$sampled_area, dat$sampled_area)
  # dat[sampled_area < 1.2e+8, hist(sampled_area)]

  # check for incorrect calculations
  # dnew[which(senst$n == 1), (plot_res * n_sites) / 10000]
  # dnew[sampled_area < 1e+9, plot((plot_res * n_sites) / 10000, sampled_area)]
  # dat[sampled_area < 1e+7, plot((plot_res * n_sites) / 10000, sampled_area)]
  # ii <- which(dat[, round((plot_res * n_sites) / 10000 - sampled_area, 4)] 
  #            != 0)
  # dat[ii, c(1:3, 8:10), with = FALSE]
  # dat[56, c(1:3, 8:10), with = FALSE]
  # dat[ii, round((plot_res * n_sites) / 10000 - sampled_area, 4)]

  # temporal variables
  dnew[which(senst$sampd == 1), samp_duration := samp_duration * d]
  dnew[which(senst$tbtwn == 1), t_btwn_samp := t_btwn_samp * e]
  dnew[, study_duration := {
    recalc_duration(study_duration, samp_duration, t_btwn_samp)
  }]
  dnew[, t_btwn_samp := to_infin_byond(t_btwn_samp)]
  # dnew[7, recalc_duration(study_duration, samp_duration, t_btwn_samp)]

  round(dat$study_duration - dnew$study_duration, 4)
  # dnew[1:20, ]
#   dnew[which(senst$n == 1), n_sites]
#   tst <- which(dat$plot_res > 1)
#   cbind(dat[tst, log10(plot_res)], dnew[tst, log10(plot_res)])
#   cbind(dat[which(senst$res == 1), plot_res], 
#         dnew[which(senst$res == 1), plot_res])
#   plot(dat$n_sites, dnew$n_sites)
})

# full function for resampling
resamp_func <- function(dat, p, iter) {
  bout <- lapply(1:iter, function(x) {  # x <- 1
    if((x / 100) %in% 1:100) print(x)
    # amount to perturb
    a <- runif(1, min = 1 - p, max = 1 + p)  # plot_res perturb
    b <- runif(1, min = 1 - p, max = 1 + p)  # n_sites perturb
    d <- runif(1, min = 1 - p, max = 1 + p)  # samp_duration perturb
    e <- runif(1, min = 1 - p, max = 1 + p)  # t_btwn_samp perturb

    # spatial variables
    dnew <- copy(dat[, .(plot_res, n_sites, sampled_area, samp_duration,
                         t_btwn_samp, study_duration)])
    dnew[which(senst$res == 1), plot_res := plot_res * a]
    dnew[which(senst$n == 1), n_sites := n_sites * b]
    dnew[, sampled_area := (plot_res * n_sites) / 10000]

    # temporal variables
    dnew[which(senst$sampd == 1), samp_duration := samp_duration * d]
    dnew[which(senst$tbtwn == 1), t_btwn_samp := t_btwn_samp * e]
    dnew[, study_duration := {
      recalc_duration(study_duration, samp_duration, t_btwn_samp)
    }]
    dnew[, t_btwn_samp := to_infin_byond(t_btwn_samp)]  # set high
  })
  return(bout)
}

# perturbed samples
p10 <- resamp_func(dat, 0.1, 1000)  # 10% perturb
p20 <- resamp_func(dat, 0.2, 1000)  # 20% perturb
p30 <- resamp_func(dat, 0.3, 1000)  # 30% perturb

# bootstrap
bootsamp <- lapply(1:1000, function(x) {
  if((x / 100) %in% 1:100) print(x)
  dnew <- copy(dat[, .(plot_res, n_sites, sampled_area, samp_duration,
                       t_btwn_samp, study_duration)])
  dnew <- dnew[sample(1:.N, size = .N, replace = TRUE), ]
  dnew[, t_btwn_samp := to_infin_byond(t_btwn_samp)]  # set high
  dnew
})

# plot(bootsamp[[3]]$plot_res, dat$plot_res)
# plot(bootsamp[[3]]$plot_res, bootsamp[[10]]$plot_res)
# plot(bootsamp[[1]]$plot_res, bootsamp[[10]]$plot_res)
# sd(sapply(bootsamp, function(x) mean(x$plot_res)))
# mean(bootsamp[[3]]$plot_res - bootsamp[[10]]$plot_res)

# a <- 10
# b <- 10
# 
# u <- 0.2
# rnorm(100, mean = a, sd = 0.2 * a)
# a * b

# dat[t_btwn_samp == 0, t_btwn_samp := 365 * 100000]  # interval adjust

@@

### Scaling in log10 space
```{r, eval = FALSE}
i <- 0.0000001
j <- rep(0, 16)
for(k in 1:length(j)) {
  i <- i * 10
  j[k] <- i
}

# temporal scales
tdt <- data.table("scaleval" = j, "time" = j)
tdt[, tlog := log10(time)]

# labels for temporal axes
# return interval
tlab1 <- c(expression("second"^-1), expression("minute"^-1),
           expression("hour"^-1), expression("day"^-1), 
           expression("week"^-1), expression("month"^-1),            
           expression("year"^-1), expression("decade"^-1),
           expression("century"^-1), 
           expression("millenium"^-1), "once-off")# expression(infinity))
taxis1 <- cbind.data.frame( 
  c(1 / (24 * 60 * 60), 1 / (24 * 60), 1 / 24, 1, 7, 30, 365, 365 * 10, 
    365 * 100, 365 * 1000, 365 * 10000))
taxis1 <- data.table(taxis1)
setnames(taxis1, names(taxis1), "days")
taxis1[, logdays := log10(days)]

taxis2 <- cbind.data.frame(
  c("second", "minute", "hour", "day", "week", "month", "year", "decade",
    "century", "millenium", "10 KA"),  
  c(1 / (24 * 60 * 60), 1 / (24 * 60), 1 / 24, 1, 7, 30, 365, 365 * 10, 
    365 * 100, 365 * 1000, 365 * 10000))
taxis2 <- data.table(taxis2)
setnames(taxis2, names(taxis2), c("label", "days"))
taxis2[, logdays := log10(days)]

# spatial
# plot(1:10, xlab = expression(paste("mm"^2)), xaxt = "n")
# axis(1, at = 1:8, labels = lab, las = 2)

# plot resolution
alab1 <- c(expression("0.01 cm"^2), expression("0.1 cm"^2), 
           expression("1 cm"^2), expression("10 cm"^2),
           expression("100 cm"^2), expression("1000 cm"^2), 
           expression("1 m"^2), expression("10 m"^2),
           expression("100 m"^2), expression("1000 m"^2), 
           "1 ha", "10 ha", "100 ha", "1000 ha", "10000 ha")

aaxis1 <- cbind.data.frame(c(0.000001, 0.00001, 0.0001, 0.001, 0.01, 0.1,
                             1^2, 10, 10^2, 10^3, 10^4, 10^5, 10^6, 10^7, 10^8))
aaxis1 <- data.table(aaxis1)
setnames(aaxis1, names(aaxis1), "res")
aaxis1[, logres := log10(res)]

# sampled area
alab2 <- c(expression("1 m"^2), expression("10 m"^2), expression("100 m"^2),
           expression("1000 m"^2), expression("1 ha"), expression("10 ha"),
           expression("100 ha"), expression("1000 ha"), 
           expression(paste(10^4 , " ha")), expression(paste(10^5 , " ha")), 
           expression(paste(10^6 , " ha")), expression(paste(10^7 , " ha")), 
           expression(paste(10^8 , " ha")), expression(paste(10^9 , " ha")), 
           expression(paste(10^10 , " ha")))

aaxis2 <- cbind.data.frame(
  c(0.1 / 10000, 10 / 10000, 1000 / 10000, 1, 10, 10^2, 10^3, 10^4, 10^5, 10^6,
    10^7, 10^8, 10^9, 10^10))
aaxis2 <- data.table(aaxis2)
setnames(aaxis2, names(aaxis2), "area")
aaxis2[, logarea := log10(area)]

### Boot-strapped resolution versus extent
```{r, eval = FALSE}
p30dt <- rbindlist(p30)
resdat <- data.table(x = log10(p30dt$t_btwn_samp), y = log10(p30dt$plot_res))
resdat[y < min(aaxis2), y := min(aaxis2)]
resdat[y > max(aaxis2), y := max(aaxis2)]
resdat$n <- rep(1, nrow(resdat))
coordinates(resdat) <- ~x + y
rx <- range(resdat$x)
# rx <- c(floor(rx[1]), ceiling(rx[2]))
rx <- round(rx / 0.5) * 0.5  # round to nearest 0.5
rx[2] <- 7.6
ry <- range(aaxis1$logres)

rkd <- kdensity(rx[1], rx[2], ry[1], ry[2], 0.1, resdat, 0.8)

par(mar = c(5, 5, 3, 3))
# plot(rkd)
image(rkd, col = rev(terrain.colors(20)), axes = FALSE, xlab = "", 
      ylab = "", xlim = rx, ylim = ry)
axis(1, at = taxis1$logdays[-5], labels = tlab1[-5], las = 2)
axis(2, at = aaxis2$logres, labels = alab2, las = 2)

# main plot
# bootdt
# resolution
bootdt <- rbindlist(bootsamp)
resdat2 <- data.table(x = log10(bootdt$t_btwn_samp), y = log10(bootdt$plot_res))
resdat2$n <- rep(1, nrow(resdat2))
coordinates(resdat2) <- ~x + y
rx <- range(resdat2$x)
rx <- round(rx / 0.5) * 0.5  # round to nearest 0.5
rx[2] <- 6.56
# rx[2] <- 7.6

# extent
extdat2 <- data.table(x = log10(bootdt$study_duration), 
                      y = log10(bootdt$sampled_area))
extdat2$n <- rep(1, nrow(extdat2))
coordinates(extdat2) <- ~x + y
ex <- range(taxis2$logdays)
ex <- c(floor(ex[1]), 5.56)#ceiling(ex[2]))
# ex <- round(ex / 0.5) * 0.5  # round to nearest 0.5
# ex[2] <- 7.6
ey <- range(aaxis2$logarea)

# densities
# resolution
rres2 <- kdensity(rx[1], rx[2], ry[1], ry[2], 0.1, resdat2, 1)
rres2 <- (rres2 / cellStats(rres2, sum)) * 100
rng <- range(rres2[is.finite(rres2)])
bwidth <- (rng[2] - rng[1]) / 30
brks <- seq(rng[1], rng[2], bwidth)
brklabs <- seq(0, 0.1, 0.02)#round(brks[seq(1, length(brks), 5)], 2)

# extent
rext2 <- kdensity(ex[1], ex[2], ey[1], ey[2], 0.1, extdat2, 1)
rext2 <- (rext2 / cellStats(rext2, sum)) * 100
rng <- range(rext2[is.finite(rext2)])
bwidth <- (rng[2] - rng[1]) / 30
brks2 <- seq(rng[1], rng[2], bwidth)
brklabs2 <- round(brks2[seq(1, length(brks2), 3)], 2)

cxa = 0.7
pdf("paper/figures/res_v_extent_bstrap.pdf", width = 7, 
    height = 2.5)
par(mfrow = c(1, 2), mar = c(4, 4, 0.3, 3), oma = c(0, 0, 0, 1), 
    mgp = c(2, 0.5, 0))
image(rres2, col = rev(terrain.colors(30)), breaks = brks,
     axes = FALSE, xlab = "", ylab = "")
# plot(rres2, col = rev(terrain.colors(20)))
axis(1, at = taxis1$logdays[-c(5, 9, 10)], labels = tlab1[-c(5, 9, 10)], 
     las = 2, tcl = -0.2, cex.axis = cxa)
axis(2, at = aaxis1$logres, labels = alab1, las = 2, tcl = -0.2, 
     cex.axis = cxa)
# plot(rres2, axes = FALSE, legend.only = TRUE)
aargs <- list(mgp = c(3, 1, 0), at = brklabs, labels = brklabs, 
              cex.axis = cxa)
plot(rres2, legend.only = TRUE, axis.args = aargs)

image(rext2, col = rev(terrain.colors(30)), axes = FALSE, xlab = "", 
      ylab = "", breaks = brks2)
axis(1, at = taxis2$logdays[-5], labels = taxis2$label[-5], las = 2,
     cex.axis = cxa, tcl = -0.2)
axis(2, at = aaxis2$logarea, labels = alab2[-2], las = 2, cex.axis = cxa,
     tcl = -0.2)
aargs <- list(mgp = c(3, 1, 0), at = brklabs2, labels = brklabs2, 
              cex.axis = cxa)
plot(rext2, legend.only = TRUE, axis.args = aargs)
dev.off()

# image(rkd2 > qtiles[40])

v <- values(rkd2)
v <- v[(v > 0) & !is.na(v)]
qtiles <- quantile(v, probs = seq(0, 1, 0.01))
round(qtiles / sum(qtiles) * 100, 2)
sum(v[v > qtiles[19]]) / sum(v)
bootdt
sum(qtiles)

length(which(dat$study_type %in% 
               c("remote sensing", "other geographic data"))) / nrow(dat)
dat[t_btwn_samp == 0, .N] / dat[, .N]  # 31% of samples are once-offs
dat[study_duration == samp_duration, .N]

p50 <- rkd2 >= qtiles[11]
p75 <- rkd2 >= qtiles[16]

par(mfrow = c(2, 2))
bootdt[, {
  hist(log10(plot_res), main = "Plot res")
  hist(log10(t_btwn_samp), main = "Frequency")
  hist(log10(sampled_area), main = "Area")
  hist(log10(study_duration), main = "Duration")
}]

plot(rkd2)
image(rkern, add=TRUE, col=rev(terrain.colors(20)))
plot(ContourLines2SLDF(contourLines(rkern)))

dat[, {
  plot(log10(plot_res), log10(sampled_area))
  plot(log10(t_btwn_samp), log10(study_duration))
}]

points(bodmin$x, bodmin$y)
data(bodmin)
plot(bodmin$poly, asp=1, type="n")
image(kernel2d(as.points(bodmin), bodmin$poly, h0=2, nx=100, ny=100), 
      add=TRUE, col=terrain.colors(20))
plot(p50)
plot(p75)
p50poly <- rasterToPolygons(p50, dissolve = TRUE)
p75poly <- rasterToPolygons(p75, dissolve = TRUE)

plot(p50poly, col = "transparent", add = TRUE)
plot(p75poly, col = "transparent", add = TRUE)

### Resolution versus extent, gridded
```{r,eval = FALSE}
# resolution data
resdat <- data.table(x = log10(dat$t_btwn_samp), y = log10(dat$plot_res))
resdat$n <- rep(1, nrow(resdat))
coordinates(resdat) <- ~x + y
rx <- range(resdat$x)
# rx <- range(aaxis$logarea)
rx <- round(rx / 0.5) * 0.5  # round to nearest 0.5
# rx[1] <- -6.5  # set temporal interval to -6.5 to have null returns centered
# ry <- range(resdat$y)
ry <- range(aaxis$logarea)
ry <- round(ry / 0.5) * 0.5  # round to nearest 0.5

# extent data
# fix area rounded to zero in Jon's plots
extdat <- data.table("x" = log10(dat$study_duration), 
                     "y" = log10(dat$sampled_area)) 
# extdat[is.infinite(x), ]; extdat[is.infinite(y), ]

### Note: we are going to have revisit assumption of 1 day duration on 
#   sampling duration. Some people might have just put 1 day
# plot(extdat$x, extdat$y)

extdat$n <- rep(1, nrow(extdat))
coordinates(extdat) <- ~x + y
# ex <- range(extdat$x)
ex <- range(taxis2$logdays)
ex <- round(ex / 0.5) * 0.5  # round to nearest 0.5
# ex[1] <- -5
ey <- range(extdat$y)
ey <- round(ey / 0.5) * 0.5  # round to nearest 0.5

# density rasters
# vary the kernel size about them
kernsl <- lapply(c(0.4, 0.6, 0.8, 1), function(x) {
  rr <- kdensity(rx[1], rx[2], ry[1], ry[2], 0.1, resdat, x)
  er <- kdensity(ex[1], ex[2], ey[1], ey[2], 0.1, extdat, x)
  kerns <- list("res" = rr, "ext" = er)
})

# have a look
# par(mfrow = c(2, 1))
# plot(er)
# par(mar = c(3, 3, 3, 5))
# plot(er, axes = FALSE, add = FALSE, legend = FALSE, box = FALSE)
# image(er, col = rev(terrain.colors(100)), axes = FALSE, xlab = "", ylab = "")
# plot(er, legend.only = TRUE)
# axis(1, at = taxis$logdays, labels = taxis$label, las = 2)
# axis(2, at = -5:10, las = 2)
# points(extdat$x, extdat$y)
# plot(rr)
# points(resdat$x, resdat$y)

### Plot
#### Varying kernel sizes
```{r, eval = FALSE}
# As separate plots
pdf("paper/figures/res_v_extent_ksize.pdf", width = 7, height = 12, )
par(mfrow = c(4, 2), oma = c(2, 2, 0, 0), mar = c(4, 4, 4, 4))
lapply(kernsl, function(x) {
  # x <- kernsl[[1]]
  image(x$res, col = rev(terrain.colors(100)), axes = FALSE, xlab = "", 
        ylab = "", ylim = range(aaxis$logarea))
  axis(1, at = taxis1$logdays, labels = tlab1, las = 2)
  # axis(1, at = taxis$logdays, labels = taxis$label, las = 2)
  axis(2, at = aaxis$logarea, labels = alab1, las = 2)
  plot(x$res, axes = FALSE, legend.only = TRUE)
  image(x$ext, col = rev(terrain.colors(100)), axes = FALSE, xlab = "", 
        ylab = "")
  axis(1, at = taxis2$logdays, labels = taxis2$label, las = 2)
  axis(2, at = aaxis$logarea, labels = alab1, las = 2)
  # axis(2, at = ey[1]:ey[2], las = 2)
  plot(x$ext, legend.only = TRUE)
})
par(xpd = NA)
xx <- grconvertX(0.5, from = "ndc", to = "inches")
ii <- c(0.4, 0.6, 0.8, 1)
yy <- c(0.95, 0.75, 0.5, 0.25)
# yy <- c(-1, -5, -10, -20)
for(i in 1:length(ii)) {
  y <- grconvertY(yy[i], from = "ndc", to = "inches")
  # text(x = xx, y = y, labels = paste("kernel =", ii[i]))
  # par(xpd = NA)
  # mtext(text = paste("kernel =", ii[i]), side = 3, line = yy[i])
}
dev.off()

# plot(rrs, xlim = c(-5, 15), ylim = c(-5, 15), 
#      xlab = "Sample interval - log10(days)", 
#      ylab = "Plot resolution - log10(m^2)")
# plot(ers, box = FALSE, xlim = c(-5, 15), ylim = c(-5, 15), 
#      xlab = "Study duration - log10(days)", ylab = "Sampled area - log10(ha)")
# dev.off()
```
